Generality in food webs scales with species richness, not latitude

### 2015-04-10 manuscript/latitudepaper.tex
Took a section of results out of the discussion
Figures updated, just need to add final round of changes and we're good to go!

\subsection*{Scaling Relationships with $S$ and Latitude}

  When considering the relationships between species richness and all response variables 
  (link density, generality, vulnerability, and proportions of basal resources, intermediate consumers, and top predators), equation~(\ref{Loglog}) had a
  lower AIC than did equation~(\ref{Power}). This indicates that the
  data support an assumption of multiplicative lognormal error better than an
  assumption of additive normal error. That is, models where $\epsilon$ is
  modelled as an additive term on
  the logarithmic scale provide a better description of the data than models
  where $\epsilon$ is modelled as an additive term on the arithmetic scale.  
  We therefore used logarithmic-form models when assessing the
  effect of latitude on scaling relationships  with $S$.

@@

@@

   $B$ increased towards the poles ($\alpha_{Latitude:Stream}$=0.012, $p$\textless0.001)
   $T$ decreased towards the poles in stream food webs ($\alpha_{Latitude}$=0.001, $p$=0.136;
  $\alpha_{Latitude:Stream}$=-0.006, $p$=0.030)

>>>>

@@

\subsection*{Form of scaling relationships}

  When considering the relationships between species richness and proportions 
  of basal resources, intermediate consumers, and top predators and all response variables 
  (link density, generality, vulnerability), equation~(\ref{Loglog}) had a
  lower AIC than did equation~(\ref{Power}). This indicates that the
  data support an assumption of multiplicative lognormal error better than an
  assumption of additive normal error. That is, models where $\epsilon$ is
  modelled as an additive term on
  the logarithmic scale provide a better description of the data than models
  where $\epsilon$ is modelled as an additive term on the arithmetic scale.  
  We therefore used logarithmic-form models when assessing the
  effect of latitude on scaling relationships  with $S$.

@@
